Maintenance planning on French military aircraft operations

### 2017-11-21 latex/ROADEF/article_roadef_2018.tex
changes to latex document

    In order to generalize the formulation, from now on aircraft will be named "resources" and missions will be named "tasks".

@@

    The following are the possible $s \in \mathcal{S}$ states for a resource to be in any given time: Assigned to a task ('V'), Receiving maintenance ('M'), Available ('N').

@@

    These maintenances take an amount of time equal to $md_m$ periods and cannot be interrupted. The number of resources under maintenance in any given period is limited to a maximum capacity which depends on each period and is represented by $c_t$.
    % The state of the resource after exiting the maintenance period is of "as good as new" in terms of the two indicators that decide the maintenance.

@@

    \subsection{Decisions}

    The decisions involve, basically, the management of the previously defined resources. We can summarize the main decisions the following way: if resource $a$ is in state $s$ in each period $t$ and if resource $a$ is assigned to task $v$ in period $t$.

    \subsection{Parameters}

    \begin{tabular}{p{10mm}lp{110mm}}
    $c_t$            & : & number of resources that can be in maintenance in period $t$. \\
    $cd_v$           & : & resources that satisfy task's $v$ needs. \\
    $rh_{vt}$        & : & time consumed of any resource when assigned to task $v$ in period $t$. \\
    $rr_{vt}$        & : & number or resources to assign to task $v$ in period $t$. \\            
    $mu$             & : & maximum used time for each resource between maintenances. \\    
    $me$             & : & maximum elapsed time for each resource between maintenances. \\    
    $md$             & : & maintenance duration, in periods. \\        
    % $rut\_i_a$       & : & remaining used time for resource $a$ at the beginning of horizon. \\        
    % $ret\_i_a$       & : & remaining elapsed time for resource $a$ at the beginning of horizon. \\
    % $state\_i_{at}$  & : & some $s \in \mathcal{S}$ in case the resource $a$ has a fixed state. \\
    \end{tabular}
    \bigskip

@@

    \begin{tabular}{p{15mm}lp{105mm}}
        $task_{avt}$        & : & 1 if resource $a \in cd_v$ is assigned task $v$ in period $t$, 0 otherwise. \\  
        $state_{ast}$       & : & 1 if resource $a$ is assigned state $s$ in period $t$, 0 otherwise. \\  
        $start_{at}$        & : & 1 if resource $a$ starts maintenance in period $t$, 0 otherwise. \\
        $ret_{at}$          & : & remaining elapsed time (integer) for resource $a$ after period $t$. \\  
        $rut_{at}$          & : & remaining usage time (integer) for resource $a$ after period $t$. \\  
        $used_{at}$         & : & time (integer) used by resource $a$ in period $t$. \\
        $min\_avail$        & : & min number (integer) of available resources in any period. \\
        $max\_maint$        & : & max number (integer) of resources in maintenance in any period. \\
    \end{tabular}
    \bigskip

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % MAIN VARS
        %%%%%%%%%%%%%%%%%%%
        % maximum capacity:
        & \sum_{a \in \mathcal{A}} state_{ast} \leq c_{t}
                & t \in \mathcal{T}, s = 'M' \label{eq:capacity}\\
        % minimum resources
        & \sum_{a \in \mathcal{A}} task_{avt} \geq rr_{vt}
                & t \in \mathcal{T}, v \in \mathcal{V} \label{eq:taskres}\\
        % max one task per period
        & \sum_{v \in \mathcal{V}} task_{avt} \leq 1
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:maxtasks}
    \end{align}

@@

    The limit in the number of resources assigned to task and the number of resource maintenances that can be done in any given month are modeles via \ref{eq:taskres} and \ref{eq:capacity} respectively.
    Constraint \ref{eq:maxtasks} limits the number of assigned tasks for a resource to one.

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % STATES
        %%%%%%%%%%%%%%%%%%%
        % if start maintenance, at least X periods
        & state_{ast_2} \geq start_{at_1} 
                & \hspace{10mm} (t_1, t_2) \in \mathcal{T}, t_1 \leq t_2 \leq t_1 + md - 1, a \in \mathcal{A}, s = \mq{M} \label{eq:start1}\\
        % if maintenance doesn't start, we cannot have maintenance:
        & \sum_{t_1 \in \mathcal{T}} start_{at_1} \geq state_{ast_2} 
                & \hspace{10mm} (t_1) \in \mathcal{T}, t_1 \leq t_2 \leq t_1 + md - 1, a \in \mathcal{A}, s = \mq{M} \label{eq:start2}\\
        % if assigned to task: in working state
        & state_{ast} \geq task_{avt} 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, s = \mq{V} \label{eq:state1}\\
        % only one state. If we take out the 'do nothing' state, this could be \leq
        & \sum_{s \in \mathcal{S}} state_{ast} = 1 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A} \label{eq:state2}
    \end{align}

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % OBJECTIVE
        %%%%%%%%%%%%%%%%%%%
        % min available
        & min\_avail \leq \sum_{a} state_{ast}
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, s = \mq{N} \label{eq:available}\\
        % max maintenance
        & max\_maint \geq \sum_{a} state_{ast}
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, s = \mq{N} \label{eq:maintenance}
    \end{align}

@@

% \section{Conclusions et perspectives}

%     TODO.

>>>>

    The problem consists in the planning of the maintenance operations of military aircraft while complying with scheduled missions. In order to generalize the formulation, from now on aircraft will be named "resources" and missions will be named "tasks".

@@

    The following are the possible $s \in \mathcal{S}$ states for a resource to be in any given time: Assigned to a task ('V'), Receiving maintenance ('M'), Available ('A'), Needing maintenance ('N').

@@

    These maintenances take an amount of time equal to $md$ periods and cannot be interrupted. The number of resources under maintenance in any given period is limited to a maximum capacity which depends on each period and is represented by $c_t$.
    % The state of the resource after exiting the maintenance period is of "as good as new" in terms of the two indicators that decide the maintenance.

@@

    % \subsection{Decisions}

    % \subsection{Parameters}

    % \begin{tabular}{p{10mm}lp{110mm}}
    % $c_t$            & : & number of resources that can be in maintenance in period $t$. \\
    % $cd_v$           & : & resources that satisfy task's $v$ needs. \\
    % $rh_{vt}$        & : & time consumed of any resource when assigned to task $v$ in period $t$. \\
    % $rr_{vt}$        & : & number or resources to assign to task $v$ in period $t$. \\            
    % $mu$             & : & maximum used time for each resource between maintenances. \\    
    % $me$             & : & maximum elapsed time for each resource between maintenances. \\    
    % $md$             & : & maintenance duration, in periods. \\        
    % $rut\_i_a$       & : & remaining used time for resource $a$ at the beginning of horizon. \\        
    % $ret\_i_a$       & : & remaining elapsed time for resource $a$ at the beginning of horizon. \\
    % $state\_i_{at}$  & : & some $s \in \mathcal{S}$ in case the resource $a$ has a fixed state. \\
    % \end{tabular}
    % \bigskip

@@

    The decisions involve, in essence, the management of the previously defined resources. We can summarize the main decisions the following way: if resource $a$ is in state $s$ in each period $t$ and if resource $a$ is assigned to task $v$ in period $t$.

    \begin{tabular}{p{15mm}lp{105mm}}
        $task_{avt}$        & : & 1 if resource $a \in cd_v$ is assignigned task $v$ in period $t$, 0 otherwise. \\  
        $state_{ast}$       & : & 1 if resource $a$ is assigned state $s$ in period $t$, 0 otherwise. \\  
        $start_{at}$        & : & 1 if resource $a$ starts maintenance in period $t$, 0 otherwise. \\
        $ret_{at}$          & : & remaining elapsed time (integer) for resource $a$ after period $t$. \\  
        $rut_{at}$          & : & remaining usage time (integer) for remainingsource $a$ after period $t$. \\  
        $used_{at}$         & : & time (integer) used by resource $a$ in period $t$. \\
        $min\_avail$        & : & min number (integer) of available resources in any period. \\
        $max\_maint$        & : & max number (integer) of resources in maintenance in any period. \\
    \end{tabular}
    % \bigskip

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % MAIN VARS
        %%%%%%%%%%%%%%%%%%%
        % maximum capacity:
        & \sum_{a \in \mathcal{A}} state_{ast} \leq c_{t}
                & t \in \mathcal{T}, s = \mq{M} \label{eq:capacity}\\
        % minimum resources
        & \sum_{a \in \mathcal{A}} task_{avt} \geq rr_{vt}
                & t \in \mathcal{T}, v \in \mathcal{V} \label{eq:taskres}\\
        % max one task per period
        & \sum_{v \in \mathcal{V}} task_{avt} \leq 1
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:maxtasks}\\
        % if assigned to task: in working state
        & state_{ast} \geq task_{avt} 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, v \in \mathcal{V}, s = \mq{V} \label{eq:state1}\\
        % only one state. If we take out the 'do nothing' state, this could be \leq
        & \sum_{s \in \mathcal{S}} state_{ast} = 1 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A} \label{eq:state2}
    \end{align}

@@

    The limit in the number of resources assigned to task and the number of resources under maintenance that can be done in any given month are modeled via \ref{eq:taskres} and \ref{eq:capacity} respectively.
    Constraint \ref{eq:maxtasks} limits the number of assigned tasks for a resource to one.

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % STATES
        %%%%%%%%%%%%%%%%%%%
        % if start maintenance, at least X periods
        & state_{ast_2} \geq start_{at_1} 
                & \hspace{10mm} (t_1, t_2) \in \mathcal{T}, t_1 \leq t_2 \leq t_1 + md - 1, a \in \mathcal{A}, s = \mq{M} \label{eq:start1}\\
        % if maintenance doesn't start, we cannot have maintenance:
        & \sum_{t_1 \in \mathcal{T}} start_{at_1} \geq state_{ast_2} 
                & \hspace{10mm} t_2 \in \mathcal{T}, t_1 \leq t_2 \leq t_1 + md - 1, a \in \mathcal{A}, s = \mq{M} \label{eq:start2}
    \end{align}

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % OBJECTIVE
        %%%%%%%%%%%%%%%%%%%
        % min available
        & min\_avail \leq \sum_{a} state_{ast}
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, s = \mq{A} \label{eq:available}\\
        % max maintenance
        & max\_maint \geq \sum_{a} state_{ast}
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, s = \mq{M} \label{eq:maintenance}
    \end{align}

@@

\section{Conclusions et perspectives}

    The present modelization is a new way to formulate the Military Flight Planning Model. Unlike previous work, it assigns aircraft to missions, instead of just using an aggregate demand. This is useful for later improving the model by including minimum durations for mission assignment and other more complex constraints.
